---
title: "game_analysis"
author: "Yifan Wang"
date: '2022-04-02'
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# phase1: Prepare for analysis

### load packages

```{r include=FALSE}
# packages
library(tidyverse)
library(dplyr)
library(ggplot2)
library(viridis)
library(rworldmap)
```

### load data
```{r load data}
# load data
games <- read.csv('/Users/yifanwang/Desktop/vgsales.csv')

# we only use observations that have no null values
games1<- games[games$Year != "N/A",]

games1$Rank <- NULL
```

#### take a quick look of our data
```{r}
summary(games1)
```

#### show the first 10 observations
```{r}
head(games1, 10)
```


# phase2: Now we do some data analysis and make data visulization

## we will analysis the following topics
### topic overview
1. the top 5 game sales in global, North America, Japan, Europe scale
- 1.1 the top 5 game sales in global scale
- 1.2 the top 5 game sales in North America
- 1.3 the top 5 game sales in Japan
- 1.4 the top 5 game sales in Europe

2. the top 3 favorite game genres in global, North America, Japan, Europe scale
- 2.1 top 3 favorite game genres in global scale
- 2.2 top 3 favorite game genres in North America scale
- 2.3 top 3 favorite game genres in Japan scale
- 2.4 top 3 favorite game genres in Europe scale

3. for each of the top 5 popular platform, the most welcomed game (highest sales)

4. 
- 4.1 the yearly sales trend
- 4.2 genre preference in different time intervals

5. the best publisher in certain genre


### 1. the top 5 game sales in global, North America, Japan, Europe scale

#### 1.1 the top 5 game sales in global scale

```{r}
#the top 5 game sales in global scale
top5sales.global <- games1 %>% 
  # order data with descending Global_Sales
  arrange(desc(Global_Sales)) %>%
  # only select two column: Name, Global_Sales
  select(Name,Global_Sales) %>% 
  slice_head(n=5) %>%
  print
```

```{r}
ggplot(data=top5sales.global)+
  geom_bar(aes(reorder(Name, Global_Sales), Global_Sales,fill = Global_Sales), stat = 'identity') + 
  scale_fill_viridis_c() +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1,face="bold")) + labs(
    title = 'top 5 game sales in global scale',
    x = 'game',
    y = 'global sales') 
```

#### 1.2 the top 5 game sales in North America

```{r}
#the top 5 game sales in NA
top5sales.NA <- games1 %>% 
  # order data with descending Global_Sales
  arrange(desc(NA_Sales)) %>%
  # only select two column: Name, Global_Sales
  select(Name,NA_Sales) %>% 
  slice_head(n=5) %>%
  print
```

```{r}
ggplot(data=top5sales.NA)+
  geom_bar(aes(reorder(Name, NA_Sales), NA_Sales,fill = NA_Sales), stat = 'identity') + 
  scale_fill_viridis_c() +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1,face="bold")) + labs(
    title = 'top 5 game sales in North America',
    x = 'game',
    y = 'global sales') 
```

#### 1.3 the top 5 game sales in Japan

```{r}
#the top 5 game sales in Japan scale
top5sales.JP <- games1 %>% 
  # order data with descending Japan
  arrange(desc(JP_Sales)) %>%
  # only select two column: Name, Japan
  select(Name,JP_Sales) %>% 
  slice_head(n=5) %>%
  print
```

```{r}
ggplot(data=top5sales.JP)+
  geom_bar(aes(reorder(Name, JP_Sales), JP_Sales,fill = JP_Sales), stat = 'identity') + 
  scale_fill_viridis_c() +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1,face="bold")) + labs(
    title = 'top 5 game sales in Japan',
    x = 'game',
    y = 'global sales') 
```

#### 1.4 the top 5 game sales in Europe

```{r}
#the top 5 game sales in EU scale
top5sales.EU <- games1 %>% 
  # order data with descending Japan
  arrange(desc(EU_Sales)) %>%
  # only select two column: Name, Japan
  select(Name,EU_Sales) %>% 
  slice_head(n=5) %>%
  print
```

```{r}
ggplot(data=top5sales.EU)+
  geom_bar(aes(reorder(Name, EU_Sales), EU_Sales,fill = EU_Sales), stat = 'identity') + 
  scale_fill_viridis_c() +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1,face="bold")) + labs(
    title = 'top 5 game sales in Europe',
    x = 'game',
    y = 'global sales') 
```

### 2. the top 3 favorite game genres in global, North Aemerica, Japan, Europe scale

we want to know is there any difference of game genre preference among difference areas. For now, we use the amount of sales to decide if a genre is welcomed.

#### 2.1 top 3 favorite game genres in global scale

```{r}
top3genre.global <- games1 %>%
  group_by(Genre) %>%
  summarise(genre.sales = sum(Global_Sales)) %>%
  arrange(desc(genre.sales)) %>%
  slice_head(n=3) %>%
  print
```

```{r}
ggplot(data=top3genre.global)+
  geom_col(aes(reorder(Genre, genre.sales), genre.sales,fill = genre.sales), stat = 'identity') + 
  scale_fill_viridis_c() +
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 10, hjust = 1,face="bold")) + labs(
    title = 'top 3 favoriate game genres in global',
    x = 'Genre') 
```

#### 2.2 top 3 favorite game genres in North America 

```{r}
top3genre.NA <- games1 %>%
  group_by(Genre) %>%
  summarise(genre.sales = sum(NA_Sales)) %>%
  arrange(desc(genre.sales)) %>%
  slice_head(n=3) %>%
  print
```

```{r}
ggplot(data=top3genre.NA)+
  geom_col(aes(reorder(Genre, genre.sales), genre.sales,fill = genre.sales), stat = 'identity') + 
  scale_fill_viridis_c() +
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 10, hjust = 1,face="bold")) + labs(
    title = 'top 3 favoriate game genres in North America',
    x = 'Genre') 
```

#### 2.3 top 3 favorite game genres in Japan

```{r}
top3genre.JP <- games1 %>%
  group_by(Genre) %>%
  summarise(genre.sales = sum(JP_Sales)) %>%
  arrange(desc(genre.sales)) %>%
  slice_head(n=3) %>%
  print
```

```{r}
ggplot(data=top3genre.JP)+
  geom_col(aes(reorder(Genre, genre.sales), genre.sales,fill = genre.sales), stat = 'identity') + 
  scale_fill_viridis_c() +
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 10, hjust = 1,face="bold")) + labs(
    title = 'top 3 favoriate game genres in Japan',
    x = 'Genre') 
```

#### 2.4 top 3 favorite game genres in Europe

```{r}
top3genre.EU <- games1 %>%
  group_by(Genre) %>%
  summarise(genre.sales = sum(EU_Sales)) %>%
  arrange(desc(genre.sales)) %>%
  slice_head(n=3) %>%
  print
```

```{r}
ggplot(data=top3genre.EU)+
  geom_col(aes(reorder(Genre, genre.sales), genre.sales,fill = genre.sales), stat = 'identity') + 
  scale_fill_viridis_c() +
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 10, hjust = 1,face="bold")) + labs(
    title = 'top 3 favoriate game genres in Europe',
    x = 'Genre') 
```

### 3. for each of the top 5 popular platform, the most welcomed game (highest sales)

#### the top 5 popular platform

```{r}
popular5platfrom <- games1 %>%
  group_by(Platform) %>%
  summarise(genre.sales = sum(Global_Sales)) %>%
  arrange(desc(genre.sales)) %>%
  slice_head(n=5) %>%
  print
```

```{r}
ggplot(data=popular5platfrom, mapping = aes(x = Platform, y = genre.sales)) + 
  geom_segment(aes(xend=Platform, yend=0, color = Platform), size = 2.3, alpha = .8) +
  geom_point(mapping = aes(fill = Platform), size = 7, shape = 21) + 
  geom_line(group = 1, size = 1.1, linetype = 10, color = "black") +
         xlab("") +
         ylab("") +
         ggtitle("the top 5 high sales platforms in the world") +
         theme_minimal() +
         theme(plot.title = element_text(size = 20, face = "bold", hjust = .5),
               axis.title.x = element_text(size = 16, hjust = .5, face = "italic"),
               axis.title.y = element_text(size = 16, hjust = .5, face = "italic"),
               axis.text.x = element_text(size = 20, face = "bold"),
               axis.text.y = element_text(size = 20, face = "bold"),
               legend.position = "none")
```

```{r}
popular5platfrom <- popular5platfrom$Platform
```

#### the most welcomed game on each top 5 populor platform

```{r}
welcomedGames.platform <- data.frame()

for (i in 1:5){
  game.plat <- games1 %>%
    filter(Platform == popular5platfrom[i]) %>%
    arrange(desc(Global_Sales)) %>%
    slice_head(n=1) %>%
    select(Platform,Name,Global_Sales)
  
  welcomedGames.platform <- rbind(welcomedGames.platform, game.plat)
}

print(welcomedGames.platform)
```

### 4.

```{r}
# we want to show how many games were published in a given year
freq_year <- data.frame(cbind(Frequency = table(games1$Year), Percent = prop.table(table(games1$Year)) * 100))
freq_year <- freq_year[order(freq_year$Frequency, decreasing=TRUE), ]
freq_year
```
we notice that there isn't enough data after 2017. This may result from un-undated data or something else. We simply ignore data after 2017 for this part.

#### 4.1 the yearly sales trend

```{r}
sales.year <- games1 %>% 
  # only use games published before 2017
  filter(as.double(Year)<2017) %>%
  group_by(Year) %>%
  summarise(year_sales = sum(Global_Sales)) %>%
  print
```

```{r}
ggplot(data=sales.year) +
  geom_line(mapping = aes(x=as.double(Year), y=year_sales)) + 
  theme_minimal() + 
  theme(axis.text.x = element_text(size = 10, hjust = 1,face="bold")) + labs(
    title = 'the yearly sales trend',
    x = 'Year', y= 'global sales') 
```
Here, we can see that there is a decreasing sales after 2008. This trend may result from technology upgrade. New games are published in some new platform, such as PS4 PS5. Our data don't include these new data. New data may be required to make a better analysis for this topic.

#### 4.2 genre preference in different time intervals

```{r}
games1 %>% 
  # only use games published before 2017
  filter(as.double(Year)<2017) %>%
  # set year interval = 4 year
  # can be changed
  mutate(ranges = cut(as.numeric(Year),
                      seq(1980, 2016, 4))) %>% 
  group_by(ranges,Genre) %>%
  summarise(sales = sum(Global_Sales)) %>%
  arrange(desc(sales),.by_group = T) %>%
  slice_head(n=1)
```

We do see differences of game genre preference during different times.

### 5. the best publisher in certain genre
```{r}
games1 %>%
  group_by(Genre, Publisher) %>%
  summarise(sales = sum(Global_Sales)) %>%
  arrange(desc(sales),.by_group = T) %>%
  slice_head(n=1)
```
